---
title: "Home Work 11"
author: "Vitaly Briker"
date: "July 24, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Overview
Doing Data Science - Preparing Data
Live session Unit 11 assignment

#Question 1 - Brief Financial Data

#A - part

```{r}
#Load Libraries
library(tidyverse)
library("fpp2")
library("dygraphs")
library("xts")

#pull  DAX index
dax=EuStockMarkets[,1]
class(EuStockMarkets)
start(EuStockMarkets)
end(EuStockMarkets)
```

#B - part
```{r}

```

#C - part
```{r}

```

#D - part
```{r}

```

#Question 2 - 2. Cleaning and Bringing in New Features

#A,B,C - part

```{r}
sum_table=merge(va_sum,data2,by="State",all=FALSE)  #merge tables by State, remove 

sum_table$Centerper1k = sum_table$Facility_Type_Frequency*1000/sum_table$SqMiles # calculate new variable med per sqfeet
sum_table
```

#D - part

```{r}
Region=sum_table$Region # create region varibale for graph
ggplot(data=sum_table, aes(y=sum_table$Centerper1k, x=sum_table$State,fill=Region)) +
  geom_bar(stat="identity",width=0.8)+
  theme_minimal()+
  theme(
    plot.title = element_text(color="Blue", size=10, face="bold.italic"),
    axis.title.x = element_text(color="black", size=12, face="bold"),
    axis.title.y = element_text(color="black", size=12, face="bold"),
    axis.text.x=element_text(color="blue", size=8, angle=45),
    axis.text.y=element_text(color="blue", size=8))+
  ggtitle("Veterans Administration medical centers in the mainland United States per 1000 sqMiles") +
  ylab("Rate of Medical Centers") + xlab("State")+
  theme(plot.title = element_text(hjust = 0.5))
```


e. What patterns do you see? By this metric, is there any region that seems relatively
high for VA medical centers per thousand square miles? How about low? Given these
data, what advice might you give your boss before you start modeling (and why)?

#E - part

```{r}
# Based on the collected data and analysis below is the conclusion 
# North East region defently has higher rate of medical centers per squred mile however on # West side the density of medical centers is very low. I recommend to invest into West as well as South sides to create new centers.   
```




